Detecting Facial Expressions in Professional Tennis Matches

### 2017-06-27 Report06-12.Rmd
Section Headings
changed the nme of section headings

####Selecting the software
The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'

@@

####Software Recognition
The software choices allowed for POST requests to be sent via the internet. To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/animetrics.R], Microsoft^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/microsoftAPI.R] and Skybiometry^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/autoSkybiometry.R]. These scripts contained loops that would move through the images, individually posting a request for each image to be analysed. These scripts included retrieving the information provided and converting it into a usable format for our analysis.
One interesting anomaly was found when using the Skybiometry software as it limited the amount of requests per minute. We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.

@@

## Regression

@@

### Discussion
Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis. According to Table 4 Google had 38.23% of the 9.66% potential face boxes not annotated manually.
It was considered that this may have shown Google's API may have been finding more unwanted faces than the other software. However, visual inspection showed that these were actually faces. This is considered in Table 6, which showed that some of the faces were found in a crowd setting. Therefore some of these could be considered irrelevant, possibly being crowd faces. These were deemed unlikely to be detected and neglected during manual annotation. 
Interestingly, Animetrics had the least amount of matches to Manually annotated faces. Looking into this further showed that Animetrics results contained potential Face Bounding Boxes that did not contain faces.

@@

## Conclusions 
Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
This product - cost in relation
Ease of access - API calling

>>>>

####Software Selection
The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'

@@

####Software Interaction
The software choices allowed for POST requests to be sent via the internet. To access the APIs through R we enlisted the httr package, using functions from this package a script was written for Google, Animetrics^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/animetrics.R], Microsoft^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/microsoftAPI.R] and Skybiometry^[https://github.com/mvparrot/face-recognition/blob/master/SoftwareRequestScripts/autoSkybiometry.R]. These scripts contained loops that would move through the images, individually posting a request for each image to be analysed. These scripts included retrieving the information provided and converting it into a usable format for our analysis.
One interesting anomaly was found when using the Skybiometry software as it limited the amount of requests per minute. We accounted for this by stalling the posts for the amount of waiting time the software notified, and checking until the time lapsed and the script could continue looping.

@@

### Modelling Face Detection Probabiity

@@

### Results Overview
Graph 1, the Bar Chart of the Face Bounding Boxes promotes Google as the best possible software for a facial recognition application in tennis. According to Table 4 Google had 38.23% of the 9.66% potential face boxes not annotated manually.
It was considered that this may have shown Google's API may have been finding more unwanted faces than the other software. However, visual inspection showed that these were actually faces. This is considered in Table 6, which showed that some of the faces were found in a crowd setting. Therefore some of these could be considered irrelevant, possibly being crowd faces. These were deemed unlikely to be detected and neglected during manual annotation. 
Interestingly, Animetrics had the least amount of matches to Manually annotated faces. Looking into this further showed that Animetrics results contained potential Face Bounding Boxes that did not contain faces.

@@

Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
This product - cost in relation
Ease of access - API calling
